Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-05-07 MS.tex
build combined reference list

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress). Ultimately data was included from 108 different studies \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa, Bohlman:2006eo, Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chave:2009iy, Cochard:2007bn, Coley:1983hk, Comas:2002wt, Comas:2004jz, coomes_comparison_1998, coomes_greater_2009, cornelissen_seedling_1996, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005, King:2006dg, King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2001fj, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Read:2011du, Reich:1998ir, Reich:1998ja, Reich:1998vb, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Schulze:2006ww, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tjoelker:1999gp, Tobner:2013cv, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, walters_are_1996, Walters:1993eu, Walters:1993hf, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

@@

\bibliography{references/complete}\label{references}

>>>>

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress). Ultimately data was included from 108 different studies (starred references in bibliography).

@@

\nocite{*}
\bibliography{output/refs}\label{references}
